Different populations agree on which moral arguments underlie which opinions

### 2021-03-03 rscripts/manuscript-results.Rmd
accepted version

# ggsave("fig1_us-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)

@@

# ggsave("fig2_us-scatter-by-groups.jpeg", width = 180, height = 100,
#        units = "mm", dpi = 300)

@@

# ggsave("fig3_uk-arg-applicability.jpeg", width = 180, height = 80, units = "mm", dpi = 300)

@@

# ggsave("fig4_uk-scatter-by-groups.jpeg", width = 85, height = 70, units = "mm", dpi = 300)

@@

# ggsave("fig5_scatter-by-cntry.jpeg", width = 180, height = 120,
#        units = "mm", dpi = 300)

@@

>>>>

# ggsave("fig1_us-arg-applicability.eps", 
#        width = 180, height = 80, units = "mm")

@@

# ggsave("fig2_us-scatter-by-groups.eps", pl,
#        device = cairo_ps, fallback_resolution = 600,
#        width = 180, height = 100,
#        units = "mm")

@@

# ggsave("fig3_uk-arg-applicability.eps", width = 180, height = 80, units = "mm")

@@

# ggsave("fig4_uk-scatter-by-groups.eps", pl,
#        device = cairo_ps, fallback_resolution = 600,
#        width = 120, height = 100, units = "mm")

@@

# ggsave("fig5_scatter-by-cntry.eps", 
#        device = cairo_ps, fallback_resolution = 600,
#        width = 180, height = 120,
#         units = "mm")
```

@@

# The results in the manuscript are negligibly different due to using a different seed value
